A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-08-11 docs/abstract_v1.01.tex
Small change in abstract.

According to the long-slit major axis stellar kinematics from \citet{SWELLSV}, J1331 has a counter-rotating stellar core inside $\sim 2$ arcsec. We model the observed stellar kinematics in J1331's central regions by finding MGE models for the surface brightness, stellar and dark matter distribution that solve the axisymmetric Jeans equations. We test galaxy models for (A) mass-follows-light with velocity anisotropy, (B) an increasing mass-to-light ration gradient, (C) the best fit lens model, and (D) including an NFW dark matter halo. We show that, because model (A) fails to reproduce the observed kinematics, J1331 requires a steep total mass-to-light ratio gradient in the center. Model (B) predicts independently the same total mass inside the Einstein radius as the lens model, and vice versa model (C) gives an independent prediction of the observed kinematics in the galaxy center. We constrain the NFW halo of J1331 in model (D) to have a virial velocity $v_{200} \simeq 240 \pm 40$ km/s and a concentration of $c_{200} \simeq 8 \pm 2$ in case of a moderate tangential velocity anisotropy of $\beta_z \simeq −0.4 \pm 0.1$. The NFW halo models can successfully reproduce the signatures of J1331's counter-rotating stellar core and predict J1331's rotation curve at larger radii. However, all these models were more massive than expected from the gas rotation curve at larger radii, and failed to reproduce the steep drop in measured velocity dispersion at [TO DO: WHAT RADIUS???]. This could indicate a non-trivial re-distribution of matter due a possible minor merger event in J1331's past.

>>>>

According to the long-slit major axis stellar kinematics from \citet{SWELLSV}, J1331 has a counter-rotating stellar core inside $\sim 2$ arcsec. We model the observed stellar kinematics in J1331's central regions by finding MGE models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations. We find that J1331 requires a steep total mass-to-light ratio gradient in the center to reproduce the observed stellar kinematics. The best fit dynamical model predicts a total mass inside the Einstein radius consistent with the lens model, and vice versa the lens model gives an successful prediction for the observed kinematics in the galaxy center. For a dynamical model including a NFW dark matter halo,  we constrain the halo to have virial velocity $v_{200} \simeq 240 \pm 40$ km/s and a concentration of $c_{200} \simeq 8 \pm 2$ in case of a moderate tangential velocity anisotropy of $\beta_z \simeq −0.4 \pm 0.1$. The NFW halo models can successfully reproduce the signatures of J1331's counter-rotating stellar core and predict J1331's rotation curve at larger radii. However, all these models were more massive than expected from the gas rotation curve at larger radii, and failed to reproduce the steep drop in measured velocity dispersion at [TO DO: WHAT RADIUS???]. This could indicate a non-trivial re-distribution of matter due a possible minor merger event in J1331's past.
